---
title: "Project1"
author: "Noone"
date: "1/22/2020"
output: html_document
---
<!--- Begin styling code. --->
<style type="text/css">
/* Whole document: */
body{
  font-family: "Palatino Linotype", "Book Antiqua", Palatino, serif;
  font-size: 12pt;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author {
  font-size: 18px;
  text-align: center;
}
h4.date {
  font-size: 18px;
  text-align: center;
}
</style>
<!--- End styling code. --->

<font size="6"> Suggestions on Producing Board Game in China </font>

If you want to earn money through building your own broad game, you should publish your game especially in China. Why? Broad game is already a traditional industry in foreign countries, and there are many excellent games, especially the type of strategy; however, relative circle in China is very small. So take your chance.

Here I conclude six gists you should pay attention to, because it’s a hard start if you want money in your pocket this way.

### **Be Prepared for your expansion**

The following two graphics show the comparison of ratings between board game and board game expansion. 

<img src = "rating_year1.jpg" alt="some text"  width="500" height="500">
<img src = "rating_year2.jpg" alt="some text"  width="750" height="650">

##### **Two graphs from session 1, corresponding to rating_year1 and rating_year2**

These two graphics show the relationship between users’ rating and the year of publishing. You might be not able to see the distinction of rating on the first graph cause they are mostly overlapped, but notice those three points, they stand for the series of game “Realms” and its expansion. It’s clear that these three expansions were published later than its board game; however, users graded them a better score. Thus, the overall score would be higher, which cause that users buy your board game just because of your expansions. 

And it always works. See the second graph. It’s very easy to conclude the mean score of expansion is greater than the mean of just board game. Since expansion is one of components of a board game, you cannot ignore it.

### **Pay Attention to The Circumstance of The World**

If you don’t know what to choose as your game topic. Look around the world. You might find something useful.

<img src = "4kinds.jpg" alt="some text"  width="500" height="500">


##### **graph from session 2, corresponding to amount_wargame**

This graph show the relationship between the year of publishing and types of game, aiming to show you the importance of adapting to the times. The density means how many of that type of board game were published during that period of years.

On September 2, 1945, the Japanese government signed an unconditional surrender certification to the United States, China, Britain and the Soviet Union on the deck of the American warship Missouri. After that, the Second World War came to the end and all involved countries went into a period of economy recovery. Economic Board game came to the world, but with a little influence. Then, people were trying to imagine the future world, the fantasy board game came up and reach the climax around 1980, but it went down quickly. Board games with the theme of western America did have some influences for kind of reasons, but it was inconsistent. However, war board game like a crane standing among chickens, although they were not published too much, they took over the market and kept that situation to the present. The point I would like to make right here is game might need to reflect the world.

<img src = "warcomp.jpg" alt="some text"  width="500" height="500">
<img src = "amount_wargame_rating_WW.jpg" alt="some text"  width="500" height="500">


##### **graph from session 2, corresponding to amount_wargame_WW and warcomp**

See how many board games were associated with World War II and that increasing rate of ratings?
The topic of war will never end. 


### **Consider the complexity of your board game.**

Your want your game to be either extremely simple or appropriate difficult. 
The following three graphics show why it is.

<img src = "gameComplex_gametype.jpg" alt="some text"  width="700" height="600">
<img src = "gameRatings_gametype.jpg" alt="some text"  width="700" height="600">


##### **graph from session 3, corresponding to gameComplex_gametype and gameRatings_gametype**

Expansion as a part of games, it has a whole new continent with a new race and a whole other story. In one word, expansion has more features, which cause that expansion has higher complexity and this brings higher rating. These two graphics show the relationship with complexity and type of game, and the relationship with rating and game type respectively. That red little point stands for mean value. It’s pretty straight forward that expansion is better in the class of complexity. 

How difficult it should be?

<img src = "gameComplex_ratings.jpg" alt="some text"  width="500" height="500">


##### **graph from session 3, corresponding to gameComplex_ratings**

This graph shows the relationship between complexity and ratings.
You can just drop off the idea of complexity, because some players do love simple game than hard game. It’s much easy for them to get started. Or, push your game to the level 3 or level 4 of complexity. That makes you game more challenge without being tedious. It’s easy to say that in the graph of expansion, there is a turning point at level 4 of complexity, which after rating goes down. In graph of board game, although the rating for level 5 complexity is higher than level 4, there are also more lower-rated games.


### **Maybe one-player form should be in your outline**

For some group of people, maybe it’s hard for them and their friends to be together, or maybe some people want to play board game to kill time. In this perspective, you should consider the minimum players of normally operating the game. 

<img src = "coopgame_rating.jpg" alt="some text"  width="500" height="500">


##### **graph from session 4, corresponding to coopgame_rating**

This graph shows the relationship between minimum players and rating.

At present, most of the table games in the market are co-operative and the score fo table games that one person can play is higher than the bottom limit of table games that many people can play. 

Based on the graph, the game with standard of minimum players 1 have not-bad lowest score and great highest score. Compare to minimum-players-5 and minimum-players-6 board game, though they have greater lowest score, their highest score were constrained.


### **Give players a break**

Here is actually an another reason for not overcomplicating your board game.

<img src = "timeplaying_rating.jpg" alt="some text"  width="500" height="500">


##### **graph from session 5, corresponding to timeplaying_rating**


These two graphs show the relationship between playing time and ratings overall on both board game and related expansion. From the red curve line, we can conclude that the higher the complexity is, the longer the playing time is, because of kinds of features of expansion. I understand all game producers would like to let players play their games, but have you ever though plays might quit just because of it takes too long?

<img src = "timeplaying_complexity.jpg" alt="some text"  width="500" height="500">


##### **graph from session 5, corresponding to timeplaying_complexity**

From this graph, Which cause that the longer the playing time is, the lower the rating would be.


### **Youshould understand players psychologically**

We first distinguish players according to different age groups. 

<img src = "minage_rating.jpg" alt="some text"  width="500" height="500">


##### **graph from session 6, corresponding to minage_rating**

It can be seen that there are some rules between minimum age and board game, but they are not obvious. The overall distribution of the average time length can be roughly estimated as normal distribution. This shows that board game mainly attract players aged 8 to 12, so I suggest you consider the characteristics of players aged 8 to 12 when designing games.

In what aspect?

<img src = "category_count_age8.jpg" alt="some text"  width="700" height="700">
<img src = "category_count_age10.jpg" alt="some text"  width="700" height="700">
<img src = "category_count_age12.jpg" alt="some text"  width="700" height="700">


##### **graph from session 6, corresponding to category_count_age8, category_count_age10, and category_count_age12**

The following three graphics conclude the numbers of each them of board game. There are reasons for the top 10 games in each age. Maybe to players age 8-10, they prefer abstract and animal games because they want to see dynamic change. To players around 12, they prefer war game as you can see war-related game all have a large circulation because they’re looking for excitement and enjoy the achievement of their logic ability.

So, Be thoughtful.

```{r, include = FALSE, echo = FALSE}
# Code Appendix

#-----------------------------------------------------------------------------------------------------------------------------------------
library("tidyverse")
library("splitstackshape")
library("ggplot2")
library("ggpubr")
# Create dataframe which only includes "yearpublished" over 1950 and "users' rating" over 25
data_boardgame <- read.csv("https://raw.githubusercontent.com/bryandmartin/STAT302/master/docs/Projects/project1_bgdataviz/board_game_raw.csv", stringsAsFactors = FALSE) %>%
  filter(yearpublished >= 1950 & users_rated >= 25) %>%
  # Split category by "," in horizontal direction
  cSplit(splitCols = c("category","mechanic"), sep = c(","), direction = "wide")




#-----------------------------------------------------------------------------------------------------------------------------------------
# Session 1
# Set plot users'rating and published year
rating_year1 <- ggplot(data = data_boardgame,
       aes(x = yearpublished,
           y = average_rating,
           # Colored by game's type
           color = game_type)) +
  # Fade points
  geom_point(alpha = 0.5) +
  # Points out four relative games: 1 boardgame, 3 expansion of boardgame
  geom_point(data = data_boardgame[data_boardgame$game_id == 68606,],color = "red", size =3)+
  annotate(geom = "text", x = 2010, y = 5.5, label =  "Game") +
  geom_point(data = data_boardgame[data_boardgame$game_id == 154310,],color = "blue", size =3)+
  annotate(geom = "text", x = 2019, y = 6, label =  "Exps") +
  geom_point(data = data_boardgame[data_boardgame$game_id == 142728,],color = "blue", size =3)+
  geom_point(data = data_boardgame[data_boardgame$game_id == 152417,],color = "blue", size =3)+

  # Add a trendline
  geom_smooth(aes(group = game_type),
              se = FALSE, size = 0.5,
              color = "black",
              method = "loess") +
  
  # Set up titles, subtitles, legend of paragraph
  labs(subtitle = "Ratings for boardgame & boardgame expansion from 1950 to present",
       title = "If your board game got a lower score, expansion is the savior",
       x = "year published",
       y = "Users' rating",
       legend = "Game Type",
       color = "Game Type",
       caption = "Resouce: Boardgamegeek.com") +
  
  # Set font and size of title and subtile and spacing between each graph
  theme(plot.title = element_text(hjust = 0.3,
                                  face = "bold",
                                  size = 14),
        plot.subtitle = element_text(hjust = 0.5))
  

# Set up label that contains new board name
labels <- c(boardgame = "Board Game", boardgameexpansion = "Board Game Expansion")
 
# Set plot by users' rating and yearbulished
# This is a seperate version of rating_year1
rating_year2 <- ggplot(data = data_boardgame,
       aes(x = yearpublished,
           y = average_rating,
           # Colored by color
           color = game_type)) +
  # Fade points
  geom_point(alpha = 0.5) +
  # Points out four relative games: 1 boardgame, 3 expansion of boardgame
  geom_point(data = data_boardgame[data_boardgame$game_id == 68606,],color = "red", size = 3) +
  geom_point(data = data_boardgame[data_boardgame$game_id == 154310,],color = "blue", size = 3)+
  geom_point(data = data_boardgame[data_boardgame$game_id == 142728,],color = "blue", size = 3)+
  geom_point(data = data_boardgame[data_boardgame$game_id == 152417,],color = "blue", size = 3)+
  # Seperate graph by game type
  facet_wrap(~ game_type) +
  
  # Add trendline and set up
  geom_smooth(aes(group = game_type),
              se = FALSE, size = 0.5,
              color = "black",
              method = "loess") +
  
  # set up titles
  labs(title = "If your board game got a lower score, expansion is the savior",
       subtitle = "Ratings for boardgame & boardgame expansion from 1950 to present",
       x = "year published",
       y = "Users' rating",
       legend = "Game Type",
       caption = "Resouce: Boardgamegeek.com") +
  
  # Set font and size of title and subtile and spacing between each graph
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = "none",
        panel.spacing = unit(0.5,"cm")) +
   # Change the board name
   facet_grid(. ~ game_type, labeller=labeller(game_type = labels))

# Call graphics
rating_year1
rating_year2

```

```{r}
#-----------------------------------------------------------------------------------------------------------------------------------------
# Session 2
# Set up dataframe by its category Wargame
data_boardgame_war <- data_boardgame %>%
  filter(category_01 == "Wargame" & (yearpublished >= 1950 & yearpublished <= 2014 ))
# Set up dataframe by its category Economic
data_boardgame_econ <- data_boardgame %>%
  filter(category_01 == "Economic" & (yearpublished >= 1950 & yearpublished <= 2014 ))
# Set up dataframe by its category American West
data_boardgame_awest <- data_boardgame %>%
  filter(category_01 == "American West" & (yearpublished >= 1950 & yearpublished <= 2014 ))
# Set up dataframe by its category Fantasy
date_boardgame_fant <- data_boardgame %>%
  filter(category_01 == "Fantasy" & (yearpublished >= 1950 & yearpublished <= 2014 ))

# Combine the following dataframe
data_boardgame_4kinds <- rbind(data_boardgame_war, 
                               data_boardgame_econ, 
                               data_boardgame_awest,
                               date_boardgame_fant)

# Use histogram plot to draw relative published games
amount_wargame <- ggplot(data = data_boardgame_4kinds,
       aes(x = yearpublished,
           color = category_01)) +
  geom_histogram(aes(y= ..density..),
                 bins = 20,
                 color = "white",
                 fill = "gray30",
                 alpha = 0.5) +
  # Seperate graph by new category_01
  facet_wrap(~ category_01) +
  # Add density line
  geom_density(color = "black") +
  # Set background white
  theme_bw() +
  # Set font and size of title and subtile
  theme(plot.title = element_text(face = "bold",
                                  size = 14),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold")) +
  
  # set up titles
  labs(x = "Amount of Published games",
       y = "Density of amount",
       title = "Your board games need to adapt to the times",
       subtitle = "Amount of 4 kinds of game published from 1950 to 2015",
       caption = "Resouce: Boardgamegeek.com")

# Create World War I dataframe
data_boardgame_warWW1 <- data_boardgame %>%
  filter(category_01 == "Wargame" & category_02 == "World War I" & (yearpublished >= 1950 & yearpublished <= 2015 & average_rating > 5.5))

# Create World War II dataframe
data_boardgame_warWW2 <- data_boardgame %>%
  filter(category_01 == "Wargame" & category_02 == "World War II" & (yearpublished >= 1950 & yearpublished <= 2015 & average_rating > 5.5))

# Combine these two dataframe
date_boardgame_warWW <- rbind(data_boardgame_warWW1,data_boardgame_warWW2)


# Boxplot. About WW2 war game and its mean value
amount_wargame_rating_WW <- ggplot(data = data_boardgame_warWW2,
       aes(x = yearpublished,
           y = average_rating,
           # Colored by game's type
           color = game_type)) +
  # Fade points
  geom_point(alpha = 0.5) +

  # Add a trendline
  geom_smooth(se = FALSE, size = 0.5,
              color = "black",
              method = "loess") +
    
  # Set up titles, subtitles, legend of paragraph
  labs(subtitle = "Ratings for boardgame & boardgame expansions with the theme of WWII",
       title = "World War II has generated impact more than on just economy",
       x = "year published",
       y = "Users' rating",
       legend = "Game Type",
       color = "Game Type",
       caption = "Resouce: Boardgamegeek.com") +
  
  # Set font and size of title and subtile and spacing between each graph
  theme(plot.title = element_text(hjust = 0.3,
                                  face = "bold",
                                  size = 14),
        plot.subtitle = element_text(hjust = 0.5))

# Barplot
amount_wargame_WW <- ggplot(data = date_boardgame_warWW, 
                            aes(x= category_02)) +
  geom_bar(stat = "count",
           color = "black", 
           fill = c("darkorchid4","brown4")) +
  
  # Set text and show the label of counts
  geom_text(stat = 'count',
            aes(label =..count.., vjust = -0.2)) +
  # Set background white
  theme_bw() +
  
  # Set up titles
  labs(x = "Game's content",
       y = "Counts",
       title = "World War II has generated impact more than on just economy",
       subtitle = "Counts of WW I and WW II games published from 1950 to 2010",
       caption = "Resouce: Boardgamegeek.com") +
  
  # Set Set font and size of title and subtile
  theme(plot.title = element_text(face = "bold",
                                  size = 14),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold"))

# Save graphics as pdf.


#Call the following graphics
amount_wargame
amount_wargame_WW
amount_wargame_rating_WW
```

```{r}
#-----------------------------------------------------------------------------------------------------------------------------------------
# Session 3
#(ggpubr)

# Plot. By game type and average complexity
gameComplex_gametype <- ggplot(data = data_boardgame,
                     aes(x = game_type, 
                         y = average_complexity,
                         group = game_type)) +
  geom_boxplot(outlier.colour="snow4",
               aes(color = game_type)) +
  
  # Show the mean value of boxplot 
  stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="red", fill="red") +
  
  # Set background white
  theme_bw() +
  
  # Set up title
  labs(title = "Proper difficulty is better",
       subtitle = "complexity of game versus. game type",
       x = "game type",
       y = "complexity of game") +
  
  # Reverse the x-axis and y-axis
  coord_flip() +
  
  # Set up title's font and size and positions
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14))



# Plot. By game type and average rating
gameRatings_gametype <- ggplot(data = data_boardgame,
                     aes(x = game_type, 
                         y = average_rating,
                         group = game_type)) +
  geom_boxplot(outlier.colour="snow4",
               aes(color = game_type)) +
  
  # Show the mean value of boxplot
  stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="red", fill="red") +
  
  # Set background white
  theme_bw() +
  
  # Set up titles 
  labs(title = "Proper difficulty is better",
       subtitle = "Users'rating versus. game",
       x = "game type",
       y = "Users' rating",
       caption = "Resouce: Boardgamegeek.com") +
  
  # Reverse x-axis and y-axis
  coord_flip() +
  
  # Set up title's font and size and positions
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14))

# Set up labels for board name
labels <- c(boardgame = "Board Game", boardgameexpansion = "Board Game Expansion")

# Plot. average complexity by average rating
gameComplex_ratings <- ggplot(data = data_boardgame,
                                 aes(x = average_complexity,
                                     y = average_rating,
                                     # Grouped and colored by game type
                                     group = game_type,
                                     color = game_type)) +
  # Seperate graphics by game type
  facet_wrap(~ game_type) +
  
  # Fade points
  geom_point(alpha = 1/5) + 
  
  # Add trendline
  geom_smooth(aes(group = game_type),
              se = FALSE, size = 1.0,
              color = c("black"), method = "loess") +
  
  # Set background white
   theme_bw() +
  # Set up titles
   labs(title = "Ratings versus game's complexity",
        subtitle = "Usually, the more complexity a game is, the more higher rating it will be graded",
       x = "Game complexity",
       y = "Users' rating",
       legend = "Game Type",
       color = "Game Type",
       caption = "Resouce: Boardgamegeek.com") +
  # Set up titles' font and size
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14),
        # Remove ledengd
        legend.position = "none",
        # Change the space between each small graph
        panel.spacing = unit(0.5,"cm"),
        plot.subtitle = element_text(hjust = 0.5)) +
   # Change board game
   facet_grid(. ~ game_type, labeller=labeller(game_type = labels))
# Save the graphics as pdf
 ggsave(filename = "gameComplex_ratings.jpg", plot = gameComplex_ratings, height = 7, width = 7)
 ggsave(filename = "gameComplex_gametype.jpg", plot = gameComplex_gametype, height = 7, width = 7)
 ggsave(filename = "gameRatings_gametype.jpg", plot = gameRatings_gametype, height = 7, width = 7)
gameComplex_gametype
gameRatings_gametype
gameComplex_ratings


#-----------------------------------------------------------------------------------------------------------------------------------------
# Session 4
# Call library dplyr
library("dplyr")

# Create new dataframe that the first to the thrid mechanic is Co-operative play
data_boardgame_coop <- data_boardgame %>%
  filter(mechanic_01 == "Co-operative Play" | mechanic_02 == "Co-operative Play" | mechanic_03 == "Co-operative Play")

# Plot. By minplaers and average rating.
coopgame_rating <- ggplot(data = data_boardgame_coop,
                          aes(x = minplayers,
                              y = average_rating)) +
  # jitter plot
  geom_jitter(position = position_jitter(width = 0.01, height = 0), alpha = 1/10) +
  
  # Label the maximum and minimum value
  stat_summary(fun.y = min, colour = "orangerred", geom = "point", size = 3) +
  stat_summary(fun.y = max, colour = "royalblue", geom = "point", size = 3) +
  stat_summary(aes(label = round(..y..,2)), fun.y = min,geom= "text", size=4, hjust = -0.3) +
  stat_summary(aes(label = round(..y..,2)), fun.y = max,geom= "text", size=4, hjust = -0.3) +
  # Set background white
  theme_bw() +
  # limit x-axis scale
  xlim(1,6) +
  
  # Set titles' font and size
  theme(plot.title = element_text(face = "bold",
                                  size = 14),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold")) +
  
  # Set up titles
  labs(x = "minimum players",
       y = "Users' rating",
       title = "'minimum players' is also a consideration ",
       subtitle = "Co-operative boardgames that allow one people to play might fit the majority",
       caption = "Resouce: Boardgamegeek.com")
  
# Call graphics
coopgame_rating

#  Save graphics
ggsave(filename = "coopgame_rating.jpg", plot = coopgame_rating, height = 7, width = 7)
#-----------------------------------------------------------------------------------------------------------------------------------------
# Session 5
# Set new dataframe by playingtime that's less than 240 and greater than 1
data_boardgame_time <- data_boardgame %>%
  filter(playingtime <= 240 & playingtime >= 1)
# Plot. By average complexity and playing time
timeplaying_complexity <- ggplot(data = data_boardgame_time,
                             aes(x = average_complexity,
                                 y = playingtime,
                                 color = game_type)) + 
  
  # Point plot
  geom_point(alpha = 0.08) +
  # Add trendline
  geom_smooth(color = "red") +
  
  # Set background white
  theme_bw() +
  
  # Set up titles' font and size
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14),
        plot.subtitle = element_text(hjust = 0.5)) +
  
  # Set up titles
  labs(x = "Game Complexity",
       y = "playing time",
       title = "Overcomplicated is a negative ",
       subtitle = "Game complexity versus playing time",
       caption = "Resouce: Boardgamegeek.com")
  


# Set up new dataframe by playingtime that's greater than 1 and less than 300
data_boardgame_time <- data_boardgame %>%
  filter(playingtime <= 300 & playingtime >= 1)

# Plot. By playingtime and average rating
timeplaying_rating <- ggplot(data = data_boardgame_time,
                             aes(x = playingtime,
                                 y = average_rating)) +
  
  # Point Plot
  geom_point(alpha = 0.08) +
  # Add a trendline
  geom_smooth(color = "red") +
  # Set background white
  theme_bw() +
  # Set up titles
  labs(x = "playing time (unit: minutes)",
       y = "Users' rating",
       title = "Give players a break ",
       subtitle = "playing time versus users's rating",
       caption = "Resouce: Boardgamegeek.com") +
  
  # Set up titles' font and size
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14),
        plot.subtitle = element_text(hjust = 0.5))
# Save graphics
ggsave(filename = "timeplaying_rating.jpg", plot = timeplaying_rating, height = 7, width = 7)
ggsave(filename = "timeplaying_complexity.jpg", plot = timeplaying_complexity, height = 7, width = 7)
timeplaying_complexity
timeplaying_rating

#-----------------------------------------------------------------------------------------------------------------------------------------
# Session 6
library("dplyr")
library("tidyr")

# Create new dataframe that has minage greater than 0, less than 30 and amount of rated users over 0 but less than 15000
data_boardgame_age <- data_boardgame %>%
  filter(minage > 0 & minage <= 30 & users_rated < 15000)

# Plot. By minage
minage_rating <- ggplot(data = data_boardgame_age,
                        aes(x = minage)) +
  geom_histogram(binwidth = 1,
                 color = "white") +
  
  # Limit x-axis scale
  xlim(0,20) +
  
  # Set up titles' font and size
  theme(plot.title = element_text(face = "bold",
                                  size = 14),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold")) +
  # Set up titles
  labs(x = "minage of player",
       y = "Counts on published game on each age ",
       title = "Kids might be the main player of boardgame",
       subtitle = "Set game a good start ",
       caption = "Resouce: Boardgamegeek.com") +
  
  # Show the labels of each bin
  geom_text(stat = 'count',
            aes(label =..count.., vjust = -0.2))

minage_rating



# Create three new dataframes based on their minage
data_boardgame_age8 <- data_boardgame %>%
  filter(minage == 8 & category_01 != "NA" & category_01 != "Card Game" & category_01 != "Expansion for Base-game")

data_boardgame_age10 <- data_boardgame %>%
  filter(minage == 10 & category_01 != "NA" & category_01 != "Card Game" & category_01 != "Expansion for Base-game")

data_boardgame_age12 <- data_boardgame %>%
  filter(minage == 12 & category_01 != "NA" & category_01 != "Card Game" & category_01 != "Expansion for Base-game")

data_boardgame_age3 <- data_boardgame %>%
  filter(minage == 12 & category_01 != "NA" & category_01 != "Card Game" & category_01 != "Expansion for Base-game", minage == 8, minage == 10)

# Plot. Age8. 
category_count_age8 <- ggplot(data = data_boardgame_age8, 
                         aes(fct_infreq(category_01))) +
  geom_bar(stat = "count") +
  
  # Set background white
  theme_bw() +
  
  # Set up title's font and size
  theme(axis.text.x = element_text(size = 7,
                                   angle = 90, 
                                   hjust = 1,
                                   vjust = 0.45,
                                   face = "bold"),
        axis.ticks.x = element_line(size=1,color="red"),
        plot.title = element_text(face = "bold",
                                  size = 14)) +
  
  # Set up titles
  labs(x = "Game categories",
       y = "Counts",
       title = "Your game needs to be well-directed",
       subtitle = "Number of games with minimum age 8",
       caption = "Resouce: Boardgamegeek.com")


# Plot. Age.10
category_count_age10 <-  ggplot(data = data_boardgame_age10, 
                                aes(fct_infreq(category_01))) +
  geom_histogram(stat = "count") +
  
  # Set background white
  theme_bw() +
  
  # Set up title's font and size
  theme(axis.text.x = element_text(size = 7,
                                   angle = 90, 
                                   hjust = 1,
                                   vjust = 0.45,
                                   face = "bold"),
        axis.ticks.x = element_line(size=1,color="red"),
        plot.title = element_text(face = "bold",
                                  size = 14)) +
  # Set up titles
  labs(x = "Game categories",
       y = "Counts",
       title = "Your game needs to be well-directed",
       subtitle = "Number of games with minimum age 10",
       caption = "Resouce: Boardgamegeek.com")

  
# Plot. Age12 
category_count_age12  <- ggplot(data = data_boardgame_age12, 
                                aes(fct_infreq(category_01))) +
  geom_histogram(stat = "count") +
  
  # Set background white
  theme_bw() +
  
  # Set titles' font and size
  theme(axis.text.x = element_text(size = 7,
                                   angle = 90, 
                                   hjust = 1,
                                   vjust = 0.45,
                                   face = "bold"),
        axis.ticks.x = element_line(size=1,color="red"),
        plot.title = element_text(face = "bold",
                                  size = 14)) +
  
  # Set titles
  labs(x = "Game categories",
       y = "Counts",
       title = "Your game needs to be well-directed",
       subtitle = "Number of games with minimum age 12",
       caption = "Resouce: Boardgamegeek.com")

# Graphics
category_count_age8 
category_count_age10
category_count_age12

# save graphics
ggsave(filename = "category_count_age8.jpg", plot = category_count_age8, height = 7, width = 7)
ggsave(filename = "category_count_age10.jpg", plot = category_count_age10, height = 7, width = 7)
ggsave(filename = "category_count_age12.jpg", plot = category_count_age12, height = 7, width = 7)
ggsave(filename = "minage_rating.jpg", plot = minage_rating, height = 7, width = 7)
```
